\subsection{Software Engineer II}
\paragraph{Engineering,\href{https://censys.com}{Censys Inc},Jun 2022 -- May 2025}
\begin{itemize}
    % \item Served on Risks team developing APIs and pipelines for \href{https://censys.com/exposure-management/}{Exposure Management} product.
    \item Developed APIs, pipelines, and architecture for \href{https://censys.com/exposure-management/}{Exposure Management} and \href{censys.com/platform}{Platform} products.
    \item Created diagrams, documentation, CI/CD, protocols, and Kubernetes configs for APIs/microservices.
    \item Led development of a service that managed credits for users and organizations. A scheduled job handled credit renewal and generated daily usage reports to support product, marketing, and sales.
    \item \href{https://github.com/formancehq/ledger/commit/08f8e2aecc051fceea05d2e5b704436baf4f5005}{Contributed} to open source project \href{https://github.com/formancehq/ledger}{Formance Ledger} adding business features for credit system.
    % \item Worked with junior engineers to assign them tasks, review their code, and help them grow as engineers.
    \item Developed unique CLI to display a \href{https://github.com/charmbracelet/bubbletea}{TUI} with navigable and collapsible tree, simplifying API adoption.
    % \item Maintained applications with updated features, improved testing, bug fixes, and better abstractions.
    % \item Developed Golang microservices, aggregated data from various sources, load Postgres/Spanner databases, publish events to Google PubSub, and serve indexed data over gRPC and REST endpoints.
    % \item Developed Golang microservices interfacing with gRPC APIs, Postgres/Spanner databases, and Google Pub/Sub.
    % \item Defined Protocol Buffers, CI/CD pipelines, and Kubernetes configuration for microservices.
    % \item Worked on microservice to collect CVE exploit data from various sources for added CVE context.
    \item Created gRPC Gateway to interface between Censys and Workato to manage third-party integrations, adding dozens of new integrations and reducing development time for new integrations.
    \item Built service to poll customer networks for critical risks and update Postgres risk datastore, improving visibility into customer attack surfaces from full day refresh to minutes.
    \item Designed and developed a pipeline for CVE Risks pulling NVD and host data over gRPC, generating risk definition, posting annotations over Pub/Sub, and loading into Google Spanner.
    \item Developed efficient and hierarchical user configurations in Google Spanner using interleaved tables.
    % \item Researched new vulnerabilities and produced fingerprints to identify vulnerable systems in Censys data.
    \item Developed a procedure for fingerprinting risks that reduced code repetition and improved performance. Methodology facilitated the rapid addition of dozens of new vulnerability fingerprints.
    % \item Created library of shared code improving code quality and removing thousands of lines of tech debt.
    % \item Implemented software test suites using local containers and mocks to ensure correctness.
    % \item Built systems to contextual risk data like detect version information and present it in UI to customers.
    % \item Worked with product and marketing to describe features and highlight implications to customers.
\end{itemize}