\subsection{Software Engineer II}
\paragraph{Engineering,\href{https://www.chainguard.dev/}{Chainguard},Jun 2025 -- Present}
\begin{itemize}
    \item Implemented secure Azure account OIDC impersonation, including backend services and terraform infrastructure, to enable safe Azure account sign-in and OCI repository sync.
    \item Updated CLI tool \href{https://edu.chainguard.dev/chainguard/chainctl/}{chainctl} to manage Azure account connections and Azure Container Registry syncing.
    \item Created utility to regularly publish public \href{https://github.com/openvex}{OpenVEX} security feed to communicate vulnerability status in \href{https://www.chainguard.dev/libraries}{Chainguard Libraries}, improving the accuracy of security reporting to customers and partners.
    \item Contributed to \href{https://github.com/anchore/grype}{Grype} security scanner to utilize Chainguard OpenVEX feed to accurately define vulnerabilities in Chainguard Libraries, ensuring an open-source assessment for customer security posture.
    \item Migrated \href{https://images.chainguard.dev/security}{Chainguard Advisories} to a new V2 system with increased data fidelity and faster datastore. Validated migrated data, fixed data problems, and communicated changes to customers.
    \item Developed APIs for V2 Advisories, implementing business logic for internal teams to manage advisories and for external customers to efficiently query nearly a million security advisories.
    \item Developed TUI for managing advisories using \href{https://github.com/charmbracelet/bubbletea}{Bubble Tea} for internal teams to easily create, update, and collaborate on Chainguard Advisories, improving internal vulnerability management and tracking.
    \item Created system to modify Chainguard Helm Charts and automatically publish as \href{https://docs.aws.amazon.com/eks/latest/userguide/eks-add-ons.html}{AWS EKS Addons} to AWS Marketplace, providing customers with updated, FIPS-compliant, and secured chart addons.
\end{itemize}