\subsection{Operations Research Analyst GS-12}
\paragraph{The Research and Analysis Center,Army Futures Command,May 2017 -- Present}
\begin{itemize}
    \item Served as developer on a Combined Arms Analysis Tool for the 21st Century (COMBATXXI), a stochastic (Monte Carlo), high resolution, closed-form, discrete event combat simulation.
    \item Developed a navigation suite in Python to aid in rapid implementation of maneuver behaviors. Library estimated to save hundreds of man hours of scenario development per scenario.
    \begin{itemize}
        \item Created a graph data structure loaded from terrain, storing contextual data (trafficability, node or edge type) for nodes and edges to facilitate intelligent searching and knowledge representation.
        \item Optimized graph via functional programming approach with memoization and lazy evaluation.
        \item Implemented search methods (A*, Djikstra, Ant Colony Optimization) and heuristics.
        \item Designed path manipulation algorithms to produce unit maneuver order stacks.
    \end{itemize}
    \item Developed Python script to produce scenario alternatives for Analysis of Alternatives study from a matrix defining alternative attributes. Script estimated to save hundreds of man hours per scenario.
    \item Developed Utility AI framework in Java to enable user-defined utility measures, considerations (state variables), normalizations, aggregation (combining considerations), and selection methods.
    \begin{itemize}
        \item Performed literature review of Utility AI publications on applications to combat modeling.
        \item Implemented autonomous behaviors using utility framework, such as engagement decisions.
    \end{itemize}
    \item Developed Python script to parse wargaming tool output and generate scenario behaviors. Script uses maneuver defined in planning meetings to create scenario maneuver, rather than copying manually.
    \item Developed Java terrain reasoning methodology as sequential discrete sampling and utility evaluation.
    \begin{itemize}
        \item Utilized Terrain Reasoning to develop advanced behaviors, such as an automated tank defilade.
    \end{itemize}
    \item Led efforts to develop high-fidelity Directed Energy Weapon COMBATXXI representation. Coordinated with external agencies and shareholders to define modeling requirements and approach.
    \begin{itemize}
        \item Worked with data vendor to define data requirements and data table schema. Identified additional data required for representation in a high fidelity model and communicated needs to vendor.
    \end{itemize}
    \item Led model development for an analysis alternative study. Identified required model enhancements and model behaviors and coordinated with integration team on scenario implementation.
    % \item Initiated development of COMBATXXI reinforcement learning framework for modeling behaviors too complex for traditional integration methods.
    \item Attended military course teaching advanced Operations Research techniques and tools. Studied operations research methods including regression analysis, probability, statistical inferencing, design of experiments, mathematical programming, data cleaning, data visualization, and data analysis.
    \begin{itemize}
        % \item Conducted study to evaluate tradeoffs of Army platforms using cost models, simulations, and statistical analysis. Examined available data and scenarios to identify constraints, limitations, and assumptions. Prepared briefs covering findings and recommendations for platform acquisition.
        \item Received honor graduate recognition for exceptional performance as one of the top five students.
    \end{itemize}
    % \item Developed Python Best Practices and Style Guide for TRAC-WSMR, detailing how best to do common Python tasks.
    % \item Presented Python tips-and-tricks, including useful libraries and techniques, to members of TRAC-WSMR.
    % \item Developed Python scripts to automate laborious but common tasks. Created script to convert output of one software program into input for another, saving dozens of hours of human labor. Created script to generate many scenarios based on alternative matrix for Analysis of Alternative studies, saving hundreds of hours per study of human labor.
\end{itemize}

% Heuristics included utility-based path evaluation method to create tactically correct urban maneuvers.
% Navigation suite was used to speed up integration of combat scenarios by hundreds of hours each study.
% Developed administrative tool for COMBATXXI packaged scenarios to generate alternatives from a base scenario.
